Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-05-02 paper/main.tex
add table for AV COPEs

\paragraph{audio contrasts of parameter estimate}
% Überblick über die Kontraste geben, die tatsächlich am Ende im Paper berichtet werden -> am besten telefonisch klären
% HIER ERZÄHLEN, WARUM VIELE KONTRASTE GERCHNET WURDEN und WARUM DER EINE COPE THE ONE AND ONLY IST

\begin{table*}[t]
\caption{Contrasts of parameter estimates for the analysis of the audio-description.
\texttt{all non-geo} = all non-geo related regressors except furniture.}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrasted} & \textbf{aim/goal} \\
\midrule
1 & geo, groom > all non-geo & PPA \tabularnewline
2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
3 & room, se\_new, se\_old > all non-geo & PPA \tabularnewline
4 & geo > all non-geo & PPA \tabularnewline
5 & groom > all non-geo & PPA \tabularnewline
6 & se\_new > all non-geo & PPA \tabularnewline
7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
8 & se\_new > se\_old & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

\paragraph{video contrasts of parameter estimate}
% Überblick über die Kontraste geben, die tatsächlich am Ende im Paper berichtet werden
% ggf. irgendwo noch reinpressen, dass man damit fast alle schnitte in FG benutzt hat
We created a contrast presumably correlating with increased hemodynamic activity in the PPA by contrasting different kind of cuts. This was done without controlling for the specific visual content depicted in the frame after each cut. The cinematographic rationale was that - over the course of a movie - cuts shift from establishing the setting and the spatial relationships within a setting at the beginning of a movie to depicting persons and objects more relevant to the subsequently evolved narrative later in the movie {brown2012cinematography; mercado2011filmmakers}. The neurocientific rationale was that activity in the PPA is greater when participants view novel versus repeated scenes resp. view-points \citep{epstein1999parahippocampal}. Hence, we contrasted cuts to a setting occurring for the first time (vse\_new) and cuts within a locale depicted for the first time (vpe\_new) with shots to a recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).

\begin{table*}
\caption{COPEs for the movie.}
\begin{tabular}{lll}
\toprule
\textbf{COPE nr. } & \textbf{description} & \textbf{aim} \\
\midrule
1 & geo, rgeo, se\_new, se\_old > non\_geo & PPA \\
1 & se\_new > se\_old & PPA \\
2 & pe\_new > pe\_old & PPA \\
3 & se\_new, pe\_new > se\_old, pe\_old & PPA (the true and cool one) \\
4 & se\_new > pe\_old & PPA \\
5 & se\_new > se\_old, pe\_old & PPA \\
6 & se\_new, pe\_new > pe\_old & PPA \\
7 & pe\_new > se\_old, pe\_old & PPA \\
8 & se\_old > se\_new & DMN \\
9 & pe\_old > pe\_new & DMN \\
10 & no\_cut > se\_new, se\_old & neg. control \\
11 & no\_cut > se\_new & neg. control \\
12 & no\_cut > se\_old & neg. control \\
13 & no\_cut > pe\_new, pe\_old & neg. control \\
14 & ao: se\_new > se\_old & audio control \\
15 & ao: se\_old > se\_new & audio control \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\paragraph{audio contrasts of parameter estimate}
\todo[inline]{Warum ist COPE 1 die Nummer 1}

\begin{table*}[t]
\caption{Contrasts of parameter estimates for the analysis of the audio-description (AO).
\texttt{all non-geo} = all non-geo related regressors except furniture.}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrasted} & \textbf{aim/goal} \\
\midrule
1 & geo, groom > all non-geo & PPA \tabularnewline
2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
3 & room, se\_new, se\_old > all non-geo & PPA \tabularnewline
4 & geo > all non-geo & PPA \tabularnewline
5 & groom > all non-geo & PPA \tabularnewline
6 & se\_new > all non-geo & PPA \tabularnewline
7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
8 & se\_new > se\_old & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

\paragraph{video contrasts of parameter estimate}
% ggf. irgendwo noch reinpressen, dass man damit fast alle schnitte in FG benutzt hat
We created a contrast presumably correlating with increased hemodynamic activity in the PPA by contrasting different kind of cuts.
This was done without controlling for the specific visual content depicted in the frame after each cut.
The cinematographic rationale was that - over the course of a movie - cuts shift from establishing the setting and the spatial relationships within a setting at the beginning of a movie to depicting persons and objects more relevant to the subsequently evolved narrative later in the movie {brown2012cinematography; mercado2011filmmakers}.
The neurocientific rationale was that activity in the PPA is greater when participants view novel versus repeated scenes resp. view-points \citep{epstein1999parahippocampal}.
Hence, we contrasted cuts to a setting occurring for the first time (vse\_new) and cuts within a locale depicted for the first time (vpe\_new) with shots to a recurring setting (vse\_old) and cuts within a recurring locale (vpe\_old).

\begin{table*}[t]
    \caption{Contrasts of parameter estimates for the analysis of the audio-visual movie (AV).}
\label{tab:av-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrasted} & \textbf{aim/goal} \\
\midrule
1 & vse\_new > vpe\_old  & PPA \tabularnewline
2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
3 & vse\_new > vse\_old & PPA \tabularnewline
4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
6 & vno\_cut > vse\_new & negative control \tabularnewline
7 & vno\_cut > vse\_old & negative control \tabularnewline
8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
10 & se\_new > se\_old & control for narrator \tabularnewline
\end{tabular}
\end{table*}
